Brownian dynamics simulation of cytoplasmic dynein's powerstroke reproduces bidirectional stepping

### 2021-02-01 papers/jin-thesis/Chapters/4Results.tex
Added to thesis and changed params defaults

\section{Optimized Parameters}
\textit{Talk about best-fit parameters that matched experimentalists data. Include table with all parameters.}
\section{Stepping Patterns}
\begin{figure}[H]
	\centering
	\includegraphics[width=0.7\columnwidth]{../../plots/mc_plots/u_final_disp_probability_distribution_30.0_5.50e+09_1.00e+08_0.2_1.05_0.0_90.0_197.0_242.0}
	\includegraphics[width=0.7\columnwidth]{../../plots/mc_plots/u_step_length_1d_probability_density_30.0_5.50e+09_1.00e+08_0.2_1.05_0.0_90.0_197.0_242.0}
	\caption[Final Displacement Probability Distribution]{\textbf{Stepping Probability Distribution Plots.} \textit{Top:} Two dimensional heatmap of binding domain displacement before and after a stepping cycle. Displacement is defined as the unbounded binding domain x position minus the binded binding domain x position, calculated before and after a step. Linear regression of the probability distribution indicates a dependence the final displacement of the step and its initial displacement, similarly to experiment. \textit{Bottom:} One dimensional probability density of step length. Step length defined as final displacement minus the initial displacement. Model compared to two experimental figures of stepping patterns from \citep{Dewitt2012}.} 
	\label{fig:final_disp}
\end{figure}

%\begin{figure}[H]
%	\centering
%	\includegraphics[width=0.7\columnwidth]{../../plots/mc_plots/%u_step_length_1d_probability_density_30.0_5.50e+09_1.00e+08_0.2_1.05_0.0_90.0_197.0_242.0}
%	\caption[Step Length Histogram]{\textbf{Step Length Histogram}}
%	\label{fig:step_length}
%\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.7\columnwidth]{../../plots/mc_plots/prob_lagging_vs_init_L_-0.3563}
	\caption[Probability of Lagging Step]{\textbf{Probability of Lagging Step}}
	\label{fig:step_length}
\end{figure}

\textit{Analysis on stepping patterns and what the parameters of our model indicate. Does dynein take a lot of fast steps?}

\section{Agree with Experiment?}
\textit{Whole point of parameter fitting was to agree with Yildiz and/or other experimental data. Did we do a good job?}

>>>>

\section{Optimized Parameters}
The set of parameters that best fit Yildiz's data are shown in the table below

\begin{table}[H]
  \centering
  \begin{tabular}{|l | r | r | r|}
  	\hline
    Param & Model & Experimental & Source \\
    \hline
    $c_b$ & $\cb \Delta G_{ATP}$ &  & \\
    $c_m$ & $\cm \Delta G_{ATP}$ &  & \\
    $c_t$ & $\ct \Delta G_{ATP}$ &  & \\
    $k_b$ & $\kb s^{-1}$&  & \\
    $k_{ub}$ & $\kub s^{-1}$ & & \\
    $C$ & $\cexp$ & & \\
    $L_s$ & $\ls nm$ & $21nm$ & \cite{Burgess2003, 3vkh-cite, carter-paper}\\
    $L_t$ & $\lt nm$ & $23nm$ & \cite{Burgess2003, 3vkh-cite, carter-paper}\\
    $\theta_b$ & $\eqb$ &  120 & \cite{leschziner} \\
    $\theta_m^{\mbox{pre}}$ & $\eqmpre$ &  197 & \cite{Burgess2003}\\
    $\theta_m^{\mbox{post}}$ & $\eqmpost$ & 242 & \cite{Burgess2003}\\
    $\theta_t$ & $\eqt$ &  & \\
    $R_t$ & $\radiust$ & $8nm$ & \cite{Burgess2003}\\
    $R_m$ & $\radiusm$ & $11nm$ & \cite{Burgess2003}\\
    $R_b$ & $\radiusb$ & $3.5nm$ & \cite{Burgess2003}\\
    \hline
  \end{tabular}
  \caption{Optimized model parameters for following data sets. }
%  \caption{Parameters used in simulation. $c_b$, $c_m$ and $c_t$ are the MTBD, motor and tail spring constants, respectively. $k_b$ and $k_{ub}$ are the rates of pre-stroke to post-stroke and post-stroke to pre-stroke transitions, respectively. $L_s$ and $L_t$ are the lengths of the stalk and tail interdomain linkers. $c$ is the tension-gating factor. The $\theta$ values are the equilibrium values for each angle, where $\theta_m^{\mbox{pre}}$ is the equilibrium angle for the unbound motor in pre-stroke, whereas $\theta_m^{\mbox{post}}$ is the equilibrium angle for the bound pre-stroke motor and both post-stroke motors. $R_b$, $R_m$ and $R_t$ are the MTBD, motor and tail radii. Parameters used for all simulations unless otherwise noted}
  \label{tab:params}
\end{table}

After many trials, this combination of parameters best demonstrated the interstep correlation observed from Yildiz's experiment, while still preserving dynein's geometric constants. \textit{FIXME: Plots are wrong, need to fix and ask which plots to finalize}

\section{Stepping Patterns}
The plots that were used to compare with experiment and optimize our parameters are shown below
\begin{figure}[H]
	\centering
	\includegraphics[width=0.7\textwidth]{/mc_plots/u_final_disp_probability_distribution_30.0_5.50e+09_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
	\includegraphics[width=0.6\textwidth]{/mc_plots/u_step_length_1d_probability_density_30.0_5.50e+09_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
	\caption[Final Displacement Probability Distribution]{\textbf{Stepping Probability Distribution Plots.} \textit{Top:} Two dimensional heatmap of binding domain displacement before and after a stepping cycle. Linear regression of the probability distribution indicates a dependence between the final displacement of the step and its initial displacement. \textit{Bottom:} One dimensional probability density of step length. Step length defined as final displacement minus the initial displacement. Model compared to two experimental figures of stepping patterns from \citep{Dewitt2012}.} 
	\label{fig:DataStep}
\end{figure}
The first plot in Figure (\ref{fig:DataStep}) displayed the joint probability density of having a specific final displacement and initial displacement. The linear regression from experiment indicated the functionality between the two with an average final displacement of 9.1nm, indicated from the y-intercept. The second plot in Figure (\ref{fig:DataStep}) displayed the one-dimensional probability density of step lengths, defined as final displacement minus the initial displacement. The limitation of experiment was made very obvious here due to their inability to record short step lengths. This factor heavily influenced the parameter fitting because in order to best fit the linear correlation within steps, the model dynein had to take very fast and short steps. Since Yildiz observed a linear regression that averaged 0nm step lengths without being able to record 0nm, the model dynein was forced to take steps with very quick rebinding. The step lengths close to 0nm from Experiment Fig 3A in Figure (\ref{fig:DataStep}) were large step lengths in the off-axis.

We fit the pre-exponential unbinding factor, $C$, based on experimental probability of having a trailing (lagging) step, as shown below

\begin{figure}[H]
	\centering
	\includegraphics[width=0.7\columnwidth]{../../plots/mc_plots/prob_lagging_vs_init_L_-0.5}
	\caption[Probability of Lagging Step]{\textbf{Probability of Lagging Step}}
	\label{fig:ProbTrail}
\end{figure}

\textit{Need to include time plots and maybe more figures. Talk about the short time step.}

\section{Agree with Experiment?}
\textit{Whole point of parameter fitting was to agree with Yildiz and/or other experimental data. Did we do a good job? }

\textit{Need to eventually bring up the issue of being able to fit both the 2d hist linear regression and step length plot: If we want to fit linear regression, we must have short steps, but if we have short steps, the step length plot will not match at steps $>$ 20nm. Hard to agree with experiment when our dynein is forced to take short steps. Mention time too.}

### 2021-02-01 papers/jin-thesis/Chapters/5Conclusion.tex
Added to thesis and changed params defaults

@@

>>>>

The model has the flexibility to replicate many sets of experimental data. The most unique set is Yildiz and we were able to reproduce his observations to the best of our ability with the set of parameters we used. We discovered an inherent problem when trying to fit to data that cannot observe 0nm steps. We usec Monte Carlo that produces a smooth probability distribution because of running large numbers of simulations and law of large numbers. However, In order to best fit the linear regression, the simulation must average 0nm step lengths, meaning we need to force parameters so that model dynein takes very quick and short steps. But, if we do this, the average step length will be a lot less than what they observe and the model will not be able to achieve large steps.

@@

We can improve our model by implementing a third dimension that utilizes the off-axis. We could always run more simulations with different sets of parameters until we find the perfect set. We could implement a optimization process of maximizing and minimizing all parameters so that we get a large range of combinations and eventually narrow down to a parameter space that cleany replicates data.

### 2021-02-01 papers/paper/paper.tex
Added to thesis and changed params defaults

\section*{Plots from MC}
\begin{figure}[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/mc_plots/final_disp_probability_distribution_30.0_5.50e+09_1.00e+09_0.08_1.05_0.0_120.0_197.0_242.0_-0.3563}
\caption{\textbf{Probability distribution plot of final displacement vs. initial displacement.} Dimentions: $nm^{-2}$ (Probability per area of box).}
\label{fig:final_disp_prob}
\end{figure}

\begin{figure}[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/mc_plots/step_length_probability_distribution_30.0_5.50e+09_1.00e+09_0.08_1.05_0.0_120.0_197.0_242.0_-0.3563}
\caption{\textbf{Probability distribution plot of step length vs. initial displacement.} Dimentions: $nm^{-2}$ (Probability per area of box).}
\label{fig:step_length_prob}
\end{figure}

\begin{figure}[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/mc_plots/step_length_1d_probability_density_30.0_5.50e+09_1.00e+09_0.08_1.05_0.0_120.0_197.0_242.0_-0.3563}
\caption{\textbf{Probability density of step lengths.} Dimentions: $nm^{-1}$ (Probability per nm).}
\label{fig:step_length_prob_den}
\end{figure}

\begin{figure}[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/mc_plots/prob_lagging_vs_init_L_-0.3563}
\caption{\textbf{Probability of lagging step vs. initial L.} Dimentions: dimensionless (Probability).}
\label{fig:prob_lagging}
\end{figure}

@@

\begin{figure}[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/mc_plots/bb_time_-0.3563}
\caption{\textbf{Bothbound Time.} Dimentions: $s$ .}
\label{fig:bothbound_time}
\end{figure}

>>>>

\section*{Plots from MC}
%\begin{figure}[tbhp]
%\centering
%\includegraphics[width=\linewidth]{../../plots/mc_plots/final_disp_probability_distribution_30.0_5.50e+09_1.00e+09_0.08_1.05_0.0_120.0_197.0_242.0_-0.3563}
%\caption{\textbf{Probability distribution plot of final displacement vs. initial displacement.} Dimentions: $nm^{-2}$ (Probability per area of box).}
%\label{fig:final_disp_prob}
%\end{figure}

%\begin{figure}[tbhp]
%\centering
%\includegraphics[width=\linewidth]{../../plots/mc_plots/step_length_probability_distribution_30.0_5.50e+09_1.00e+09_0.08_1.05_0.0_120.0_197.0_242.0_-0.3563}
%\caption{\textbf{Probability distribution plot of step length vs. initial displacement.} Dimentions: $nm^{-2}$ (Probability per area of box).}
%\label{fig:step_length_prob}
%\end{figure}

%\begin{figure}[tbhp]
%\centering
%\includegraphics[width=\linewidth]{../../plots/mc_plots/step_length_1d_probability_density_30.0_5.50e+09_1.00e+09_0.08_1.05_0.0_120.0_197.0_242.0_-0.3563}
%\caption{\textbf{Probability density of step lengths.} Dimentions: $nm^{-1}$ (Probability per nm).}
%\label{fig:step_length_prob_den}
%\end{figure}
%
\begin{figure}[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/mc_plots/prob_lagging_vs_init_L_-0.5}
\caption{\textbf{Probability of lagging step vs. initial L.} Dimentions: dimensionless (Probability).}
\label{fig:prob_lagging}
\end{figure}

@@

\begin{figure}[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/mc_plots/bb_time_-0.5}
\caption{\textbf{Bothbound Time.} Dimentions: $s$ .}
\label{fig:bothbound_time}
\end{figure}
